---
title: "Event Management System Analysis"
author: "Your Name"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
library(R6)
library(readr)
library(dplyr)
library(ggplot2)
```

# Introduction

This report provides descriptive analytics on the Event Management System. The focus is on user roles, event statuses, ticket refunds, and their social and ethical implications.

# Data Loading

```{r load-data}
# Load datasets with error handling
EventAnalyzer <- R6Class("EventAnalyzer",
  public = list(
    users = NULL,
    events = NULL,
    bookings = NULL,
    registrations = NULL,
    refunds = NULL,

    initialize = function(users_path, events_path, bookings_path, registrations_path, refunds_path) {
      tryCatch({
        self$users <- read_csv(users_path)
        self$events <- read_csv(events_path)
        self$bookings <- read_csv(bookings_path)
        self$registrations <- read_csv(registrations_path)
        self$refunds <- read_csv(refunds_path)
        message("Data loaded successfully.")
      }, error = function(e) {
        stop("Error loading data: ", e$message)
      })
    },

    summarize_event_status = function() {
      self$events %>% 
        group_by(status) %>% 
        summarise(total = n()) %>% 
        ggplot(aes(x = status, y = total, fill = status)) +
        geom_col() + 
        labs(title = "Event Status Distribution", x = "Status", y = "Count")
    },

    analyze_refunds = function() {
      self$refunds %>% 
        group_by(status) %>% 
        summarise(total = n()) %>% 
        ggplot(aes(x = status, y = total, fill = status)) +
        geom_col() + 
        labs(title = "Refund Status Analysis", x = "Refund Status", y = "Count")
    },

    role_distribution = function() {
      self$users %>% 
        group_by(role) %>% 
        summarise(total = n()) %>% 
        ggplot(aes(x = role, y = total, fill = role)) +
        geom_bar(stat = "identity") + 
        labs(title = "User Role Distribution", x = "Role", y = "Number of Users")
    }
  )
)

analyzer <- EventAnalyzer$new("users.csv", "events.csv", "bookings.csv", "registrations.csv", "refunds.csv")
```

# Descriptive Analytics

## Event Status Distribution
```{r event-status}
analyzer$summarize_event_status()
```

**Interpretation**: A comparison between active and canceled events can help understand the volatility or stability in event planning.

## Refund Status Patterns
```{r refund-status}
analyzer$analyze_refunds()
```

**Insight**: This reveals the fairness of the refund system and the volume of refund handling.

## User Role Distribution
```{r user-roles}
analyzer$role_distribution()
```

**Observation**: Analyzing user engagement across different roles supports planning of user-specific features and services.

# Ethical & Social Considerations

- **Fair Refund Policy**: Ensuring transparency in cancellations and refunds builds trust.
- **Inclusive Events**: Participation across attendees and organizers reflects the inclusivity of the platform.
- **Cancellation Impact**: Frequent cancellations may reflect planning issues or social/environmental interferences.

# Conclusion

This analysis highlights key engagement trends and social implications of event management data. These insights aid in designing equitable and efficient systems for users.
